### 2019-09-06 README.Rmd
Update README

[![Travis-CI Build Status](https://travis-ci.org/nfrerebeau/archeosciences2019.svg?branch=master)](https://travis-ci.org/nfrerebeau/archeosciences2019)
[![Binder](https://mybinder.org/badge_logo.svg)](https://mybinder.org/v2/gh/nfrerebeau/archeosciences2019/master?urlpath=rstudio)

[![GitHub Release](https://img.shields.io/github/release/nfrerebeau/archeosciences2019.svg)](https://github.com/nfrerebeau/archeosciences2019/releases)

[![DOI](https://zenodo.org/badge/DOI/10.5281/zenodo.2613512.svg)](https://doi.org/10.5281/zenodo.2613512)

@@

The original manuscript was produced with R 3.5.2. See the [DESCRIPTION](DESCRIPTION) file for a full list of the packages that this project depends on, including the suggested packages. The `packrat/` directory contains the source code for all the packages we depend on. If all works well, these will be installed on your machine when you open `archeosciences2019.Rproj` in RStudio.

>>>>

[![Binder](https://mybinder.org/badge_logo.svg)](https://mybinder.org/v2/gh/nfrerebeau/archeosciences2019/master?urlpath=rstudio)
[![DOI](https://zenodo.org/badge/DOI/10.5281/zenodo.2613512.svg)](https://doi.org/10.5281/zenodo.2613512)
[![GitHub Release](https://img.shields.io/github/release/nfrerebeau/archeosciences2019.svg)](https://github.com/nfrerebeau/archeosciences2019/releases)
[![Travis-CI Build Status](https://travis-ci.org/nfrerebeau/archeosciences2019.svg?branch=master)](https://travis-ci.org/nfrerebeau/archeosciences2019)

@@

The original manuscript was produced with R 3.6.0. See the [DESCRIPTION](DESCRIPTION) file for a full list of the packages that this project depends on, including the suggested packages. The `packrat/` directory contains the source code for all the packages we depend on. If all works well, these will be installed on your machine when you open `archeosciences2019.Rproj` in RStudio.
